Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-05 article.tex
abstract

\begin{abstract}
	Given permutations $\sigma \in S_k$ and $\p \in S_n$, the Permutation Pattern (PP)
	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.
	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid 
	$213$ and $231$. 
	For the special where only $\sigma$ avoids $213$ and $231$, we present a 
	$O(kn^2)$ time algorithm. We extend our research to $(213,231)$-avoiding 
	bivincular pattern and present a $O(kn^3)$ time algorithm.
\end{abstract}

>>>>

\begin{abstract}
	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the Permutation Pattern (PP)
	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.
	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid 
	$213$ and $231$. 
	For the special where only $\sigma$ avoids $213$ and $231$, we present a 
	$O(kn^2)$ time algorithm. We extend our research to $(213,231)$-avoiding 
	bivincular pattern and present a $O(kn^3)$ time algorithm.
\end{abstract}
